Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-21 cav2017/cav2017.tex
edited sec 4.3 (on solution generalization)

We investigate two different approaches of integrating solution generalisation 
with CEGIS:
\begin{itemize}
\item[1.] The first approach uses a multi-staged validation phase
  and performs solution generalisation based on
the plant's precision, the number of loop unrollings
and the sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
\item[2.] The second approach uses abstract acceleration to compute the set of reachable states,
  which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}).

\end{itemize}

\addtodo{Revise: }
The first approach finds a controller for an individual initial state and input with a bounded time horizon and generalizes to all states, inputs and time horizons (with a final verification loop that verifies the continuous system behaviour against the previously verified discrete system bi-simulation).
The second approach finds a controller for a continuous initial state-space and input sets over an abstraction of the continuous dynamics which conforms to witness proofs at specific times k, and generalizes the solution for all times by refining the number of witnesses.

@@

\addtodo{Can we come up with some sort of figure that makes it easier to visualise
the generalisation step in each approach?}

>>>>

We investigate two different approaches of integrating solution generalisation 
with CEGIS:
\begin{itemize}
\item[1.] The first approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
  uses a multi-staged validation phase and performs solution generalisation based on
the plant's precision, the number of loop unrollings
and the sampling rate. Essentially, it finds a controller for an individual initial state
and input with a bounded time horizon and generalizes to all states,
inputs and time horizons. %% (with a final verification loop that verifies
%% the continuous system behaviour against the previously verified
%% discrete system bi-simulation)
\item[2.] The second approach described in Sec~\ref{sec:CEGIS-abstraction-refinement}
  %% uses abstract acceleration to compute the set of reachable states,
  %% which enables it to perform abstraction refinement inside the CEGIS loop.
  finds a controller for a continuous initial
state-space and input sets over an abstraction of the continuous
dynamics which conforms to witness proofs at specific times, and
generalizes the solution for all times by refining the number of
witnesses.
\end{itemize}

@@

%% \addtodo{Can we come up with some sort of figure that makes it easier to visualise
%% the generalisation step in each approach?}
